HO unification from object language to meta language

### 2024-03-27 paper/main.tex
6

\begin{definition}[reduce-to]
  A term $t$ reduce to a name $x$, if $\exists \sigma, \sigma t = x$. In
  particular, for any term $t$, $\lambda x_1 \ldots x_n.t_{x_1\ldots x_n}$
  reduces to a bound variable $x$ if one of the three following cases is
  satisfied: 1) $n = 0$ and $t = x$; 2) $t$ is the application of $x$ to a list
  of term $l$ and each $l_i$ reduces to $x_i$; 3) $t$ is a variable with scope
  $s$, and for any $bv \in [x|\vec{x}]$, it exists a $s_i$, such that $s_i$
  reduces to $bv$
\end{definition}

\begin{definition}[occurs-rigidly]
  A name $x$ occurs rigidly in a term $t$, if $\forall \sigma, \exists t' \in
  \subterm{t}, t' = x$, i.e. $x$ does not appear in the scope of any variable
  in $t$.
\end{definition}

@@

\begin{definition}[\maybeeta detection]
  For any term $t$, $\lambda x_1 \ldots x_n.t_{x_1\ldots x_n}$ is a \maybeeta if
  1) either $t$ is the application of a term with argument $l_1 \ldots l_m$ such that 
  $m \geq n$, every $l_{m-n+i}$ reduce to $x_i$, and no $l_{1\ldots m-n-1}$
  reduces to a name in $\vec{x}$; 2) or $t$ is a variable with scope $s$ and
  each $x_i$ it exists $s_j$ such that $s_j$ reduces $x_i$.
\end{definition}

>>>>

\begin{definition}[reduce-to]
  A term $t$ reduce to a name $x$, if $\exists \sigma, \sigma t = x$. In
  particular, for any term $t$, $\lambda x_1 \ldots x_n.t_{x_1\ldots x_n}$
  reduces to a bound variable $x$ if one of the three following cases is
  satisfied: 1) $n = 0$ and $t = x$; 2) $t$ is the application of $x$ to a list
  of terms $l$ and each $l_i$ reduces to $x_i$
  (since $\lambda x_1 \ldots x_n.x_{x_1\ldots x_n} = x$) ; 3) $t$ is a unification
  variable in \llambda with scope
  $s$, and for any $v \in \{ x, x_1 \ldots x_n \}$,
  there exists a $s_i \in s$, such that $s_i$ reduces to $v$
\end{definition}

\begin{definition}[occurs-rigidly]
  A name $x$ occurs rigidly in a term $t$, if $\forall \sigma, x \in
  \subterm{\sigma t}$
\end{definition}
In other words $x$ \emph{occurs-rigidly} in $t$ if it occurs in $t$
outside of the scope of unification variables since theirs instantiations
are allowed to discard their scope.

@@

\begin{definition}[\maybeeta detection]
  A term $\lambda x_1 \ldots x_n.t$ where each $x_i$ occurs in $t$ is a
  \maybeeta if
  either: 1) $t$ is a constant applied to arguments
  $l_1 \ldots l_m$ such that 
  $m \geq n$ and every $l_{m-n+i}$ reduces-to $x_i$ and
  no $x_i$ occurs-rigidly in $l_{1\ldots m-n-1}$; or 2) $t$ is a
  unification variable with scope $s$ and
  for each $x_i$ there exists a $s_j \in s$ such that $s_j$ reduces-to $x_i$.
\end{definition}
